### 2020-10-04 Analysis/Code/Paper.Rmd

```{r}
table <- texreg(texregObjects,
                stars = c(0.01, 0.05, 0.1),
                digits = 3,
                custom.model.names = c("(1)", "(2)"),
                caption = "Estimates of the Review Parameters",
                caption.above = T,
                label = "reviewEstimates")
```

@@

```{r fig.cap='\\label{scoreDifPlot} Distribution of the difference between estimated average score on and off a discount.'}
p1 <- ggplot(data = revs[, .(x = score.dif)]) +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 alpha = 0.9,
                 binwidth = 0.05,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Difference in Review Scores",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     breaks = c(0, 1, 2),
                     minor_breaks = NULL) +
  my.theme()
```

>>>>

```{r results = 'asis'}
texreg(texregObjects,
       stars = c(0.01, 0.05, 0.1),
       digits = 3,
       custom.model.names = c("(1)", "(2)"),
       caption = "Estimates of the Review Parameters",
       caption.above = T,
       label = "reviewEstimates")
```

@@

```{r fig.cap='\\label{scoreDifPlot} Distribution of the difference between estimated average score on and off a discount.'}
ggplot(data = revs[, .(x = score.dif)]) +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 alpha = 0.9,
                 binwidth = 0.05,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Difference in Review Scores",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     breaks = c(0, 1, 2),
                     minor_breaks = NULL) +
  my.theme()
```
